---
title: "Contact List De-Duplicating"
output: html_notebook
---
Enter Input File Name Here. Accepts local .xls or .xlsx files
example: infile <- "rawcontactslist.xls"
```{r}
infile <- "FILE NAME HERE"
```
Optional: Enter Output Folder Name (OutPath) and Output File (outfilename) Name Here.
```{r}
OutPath <- "FOLDERNAMEHERE"
#example: OutPath <- "C:/Users/kiana/Downloads/" - forward slashes "/" not "\"

#example: outfilename <- "cleanlist.csv"
outfilename <- "FILE NAME HERE"
```
Output File will be named same as input with _clean appended as a csv if no outfilename supplied
example:input file: "rawcontactslist.xls" 
example output file: "rawcontactslist_clean.csv"
Output file will be saved in this directory is no OutPath supplied



Deduplicating Process
```{r}
library(tidyverse)
library(readxl)

if(endsWith(infile, ".xls") | endsWith(infile,".xlsx")){
#read in the file, sheet by sheet 
for (i in 1:length(excel_sheets(infile))) {
  #read in a sheet
to_append <- read_excel(infile, sheet = i)
#add a language and id number column. id is just first number = number of sheet, then just append a 0 and the row number
to_append <- to_append %>% mutate(language = excel_sheets(infile)[i], user_id = paste(i,"0",row_number(),sep = ""))
#if reading in first sheet, just set list =, otherwise append the sheet
if(i ==1){
  rawlist <- to_append
}else{
  rawlist <- rawlist %>% bind_rows(to_append)}
}
#cleaning up and reformatting data
rawlist <- rawlist %>% pivot_longer(cols = 1:3) %>% rename(phone_type = name, number=value)
#this makes the data longer, so there is only a lang, type, id, and number column, no separate columns anymore for each type

#get rid of all the null entries
cleaned <- rawlist %>% filter(number!="NULL")
#get rid of dases in numbers
cleaned$number <- gsub("-","",cleaned$number)
#de duplicating data 
cleaned <- cleaned %>% distinct(number, .keep_all = TRUE)
#how this works is it only returns the columns where a distinct number is found. 
#it returns the first instance of the number, and leaves out the rest

#check that there are no duplicates remaining 
if(unique(duplicated(cleaned))== FALSE & length(unique(duplicated(cleaned)))==1){
  print("List De-Duped")
  #renaming columns, and changing order of columns, no actual changes made
  cleaned <- cleaned %>% rename(phone = number) %>% relocate(phone,user_id,language,phone_type) 
  
  #save to a csv
  if(outfilename == "FILE NAME HERE" | !endsWith(outfilename,".csv")){#no name supplied or incorrectedly formatted name
    filename <- sub("\\..*","",infile) %>% paste("_clean.csv",sep = "") #default output file naming 
  }else{filename <- outfilename}
  
if(OutPath == "FOLDERNAMEHERE" ){ #setting file path 
  print("no OutPath supplied, defaulted to this directory")
}else{
   if(!endsWith(OutPath,"/")){OutPath <- paste(OutPath,"/",sep = "")} #append / at end if not one already
  filename <- paste(OutPath,filename,sep = "")
  print(paste("OutPath:",OutPath))
}
  
  print(paste("output file saved:",filename))
  write_csv(cleaned,file = filename)
}
}else{print("Invalid input file")}

```